\cleardoublepage
%\pagebreak
\phantomsection
%%\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{20}
\bibitem{1} S. G. Rogelberg, C. Scott, and J. Kello, ``The science and fiction of meetings,'' MIT Sloan Management Review, vol. 48, no. 2, pp. 18–21, 2007.
\bibitem{2} K. McKeown, J. Hirschberg, M. Galley, and S. Maskey, ``From text to speech summarization,'' in Proc. IEEE Int. Conf. Acoustics, Speech and Signal Processing (ICASSP), 2005, pp. 997–1000.
\bibitem{3} G. Murray, S. Renals, and J. Carletta, ``Extractive summarization of meeting recordings,'' in Proc. European Conf. Speech Communication and Technology (Interspeech), 2005, pp. 593–596.
\bibitem{4} G. Shang et al., ``Unsupervised abstractive meeting summarization with multi-sentence compression and budgeted submodular maximization,'' in Proc. 56th Annual Meeting of the ACL, 2018, pp. 664–674.
\bibitem{5} J. Devlin et al., ``BERT: Pre-training of deep bidirectional transformers for language understanding,'' in Proc. NAACL, 2019, pp. 4171–4186.
\bibitem{6} C. Raffel et al., ``Exploring the limits of transfer learning with a unified text-to-text transformer,'' Journal of Machine Learning Research, vol. 21, no. 140, pp. 1–67, 2020.
\bibitem{7} T. Baltrusaitis et al., ``Multimodal machine learning: A survey and taxonomy,'' IEEE Transactions on Pattern Analysis and Machine Intelligence, vol. 41, no. 2, pp. 423–443, 2019.
\bibitem{8} A. Vaswani et al., ``Attention is all you need,'' in Advances in Neural Information Processing Systems (NeurIPS), 2017, pp. 5998–6008.
\bibitem{9} J. Lu et al., ``ViLBERT: Pretraining task-agnostic visiolinguistic representations for vision-and-language tasks,'' in Advances in Neural Information Processing Systems (NeurIPS), 2019, pp. 13–23.
\bibitem{10} J. Tao et al., ``Sentiment analysis with contextual multi-modal fusion,'' in Proc. ACM Multimedia, 2020, pp. 1140–1148.
\bibitem{11} F. Nihei et al., ``Predicting meeting extracts in group discussions using multimodal convolutional neural networks,'' in Proc. ACM Int. Conf. Multimodal Interaction (ICMI), 2018, pp. 421–425.
\bibitem{12} A. Graves et al., ``Neural turing machines,'' arXiv preprint arXiv:1410.5401, 2014.
\bibitem{13} M. Schlichtkrull et al., ``Modeling relational data with graph convolutional networks,'' in Proc. ESWC, 2018, pp. 593–607.
\bibitem{14} R. Trivedi et al., ``Know-Evolve: Deep temporal reasoning for dynamic knowledge graphs,'' in Proc. Int. Conf. Machine Learning (ICML), 2017, pp. 3462–3471.
\bibitem{15} C. Wu et al., ``StarSpace: Embed all the things!,'' in Proc. AAAI Conf. Artificial Intelligence, 2018, pp. 5569–5577.
\bibitem{16} R. Yan et al., ``Timeline generation: Tracking individuals on Twitter,'' in Proc. 20th Int. Conf. World Wide Web (WWW), 2011, pp. 517–526.
\bibitem{17} M. Bain et al., ``WhisperX: Time-accurate speech transcription of long-form audio,'' in Proc. Interspeech, 2023, pp. 4489–4493.
\bibitem{18} A. Radford et al., ``Robust speech recognition via large-scale weak supervision,'' in Proc. ICML, 2023, pp. 28492–28518.
\bibitem{19} K. He et al., ``Deep residual learning for image recognition,'' in Proc. IEEE Conf. Computer Vision and Pattern Recognition (CVPR), 2016, pp. 770–778.
\bibitem{20} B. McFee et al., ``librosa: Audio and music signal analysis in python,'' in Proc. 14th Python in Science Conf., 2015, pp. 18–25.
\end{thebibliography}
